Graph Topological Aspects of Granger Causal Network Learning

### 2019-07-26 paper_theory/graph_topology_granger_causality.tex
Some renaming and prepping for submission.
Essentially at the final version -- pending Ravi

\documentclass{statsoc}
% \usepackage{mathtime}
\usepackage{ccfonts,eulervm}
\usepackage{tabularx}
\usepackage{xr}
\externaldocument{proofs}
% \usepackage[T1]{fontenc}
% \usepackage[lite]{belleek}
% \fontfamily{belleek}
% \usepackage[math]{belleek}
% \usepackage{concretemath-fonts}
% \interfootnotelinepenalty=10000
% ---------------------------------------------------------------------------------------------------------------------------------
% The statsoc style file is broken?
% I have copied this code straight from stack overflow
% https://tex.stackexchange.com/questions/351768/problem-with-statsoc-class-and-pdflatex
\usepackage{geometry}

@@

% TODO: Are we, in this setting, immune to confounders?  We are removing
%       all bi-directional edges, so it seems likely that we are?  Can we state
%       any theorem about this?

@@

\def\gc{\overset{\text{GC}}{\rightarrow}}  % Granger causality arrow
\def\ngc{\overset{\text{GC}}{\nrightarrow}}  % Negated Granger causality arrow
\def\pwgc{\overset{\text{PW}}{\rightarrow}}  % Pairwise Granger causality arrow
\def\npwgc{\overset{\text{PW}}{\nrightarrow}}  % Negated pairwise Granger causality arrow
\def\te{\overset{\mathcal{T}}{\rightarrow}}  % Transfer entropy arrow
\def\gcg{\mathcal{G}}  % Granger-causality graph
\def\gcge{\mathcal{E}}  % Graph edges
\def\VAR{\mathsf{VAR}}  % VAR(p) model
\def\B{\mathsf{B}}  % Filter B
\def\wtB{\widetilde{\B}}  % General filter B
\def\A{\mathsf{A}}  % Filter A
\def\H{\mathcal{H}}  % Hilbert space

@@

\section{Introduction and Review}
\label{sec:introduction}
In this paper we study the notion of Granger-causality
\cite{granger1969investigating} \cite{Granger1980329} as a means of
uncovering an underlying causal structure in multivariate time series.
Though the underlying causality graph cannot be observed directly,
it's it's presence is inferred as a latent structure among observed
time series data.  This notion is leveraged in a variety of
applications e.g. in Neuroscience as a means of recovering
interactions amongst brain regions \cite{bressler2011wiener},
\cite{anna_paper2008}, \cite{david2008identifying}; in the study of
the dependence and connectedness of financial institutions
\cite{NBERw16223}; gene expression networks \cite{Fujita2007},
\cite{methods_for_inferring_gene_regulatory_networks_from_time_series_expression_data},
\cite{grouped_graphical_granger_modelling_for_gene_expression_regulatory_networks_discovery},
\cite{discovering_graphical_Granger_causality_using_the_truncating_lasso_penalty};
and power system design \cite{Misyrlis2016450}, \cite{yuan2014root}.

@@

The principle contributions of this paper are as follows: firstly, in
section \ref{sec:theory} we study \textit{pairwise} Granger-causality
relations, providing novel theorems connecting the structure of the
causality graph to the pairwise ``causality flow'' in the system, as
well as an interpretation in terms of the graph topology of the
sparsity pattern of matrices arising in the Wold decomposition,
generalizing in some sense the notion of ``feedback-free'' processes
studied by \cite{caines1975feedback} in close connection with
Granger-causality.  We establish sufficient conditions (sections
\ref{sec:strongly_causal_graphs}, \ref{sec:persistent_systems}) under
which a fully conditional Granger-causality graph can be recovered
from pairwise tests alone (sec \ref{sec:pairwise_algorithm}).  We
report a summary of simulation results in \ref{sec:simulation}, with
additional results reported in the supplementary material
\ref{apx:simulation}.  Our simulation results establish that there is
significant potential for improvement over existing methods, and that
the graph-topological aspects of time series analysis are relevant for
both theory and practice.  Concluding remarks on further open problems
and extensions are provided in Section \ref{sec:conclusion}.  The
proofs of each proposition and theorem are also relegated to the
supplementary material, simple corollaries have proofs included in the
main text.

@@

\begin{equation}
  \label{eq:hilbert_space_defn}
  \begin{aligned}
    \H_t^x &= \cl \{\sum_{\tau = 0}^p a_\tau^\T x(t - \tau)\ |\ a_\tau \in \R^n, p \in \N\} \subseteq L_2(\Omega)\\
    H_t^x &= \{a x(t)\ |\ a \in \R\} \subseteq L_2(\Omega),
  \end{aligned}
\end{equation}

where the closure is naturally in mean-square.  We will often omit the
superscript $x$ which should be clear from context.  Evidently these
spaces are separable, and as closed subspaces of a Hilbert space they
are themselves Hilbert.  We will denote the spaces generated in
analogous ways by particular components of $x$ as e.g.
$\H_t^{(i, j)}$, $\H_t^{i}$ or by all but a particular component as
$\H_t^{-j}$.

As a consequence of the Wold decomposition theorem (see
e.g. \cite{lindquist}), every WSS sequence has the moving average
$MA(\infty)$ representation

@@

The equations (\ref{eqn:wold}), (\ref{eqn:ar_representation}) can be
represented as $x(t) = \A(z)v(t) = \B(z)x(t) + v(t)$ via the action
(convolution) of the operators (LTI filters)
$\A(z) \defeq \sum_{\tau = 0}^\infty A(\tau)z^{-\tau}$ and
$\B(z) \defeq \sum_{\tau = 1}^\infty B(\tau)z^{-\tau}$ where the
operator $z^{-1}$ is the back shift operator acting on
$\ell_2^n(\Omega, \mathcal{F}, \mathbb{P})$, that is:

@@

\begin{definition}[Basic Setup]
  \label{def:basic_setup}
  The process $x(t)$ is an $n$ dimensional wide sense stationary
  process having invertible $\VAR(\infty)$ representation
  \eqref{eqn:ar_representation} where $v(t)$ is sequentially
  uncorrelated and has a diagonal positive-definite covariance matrix.
  The $MA(\infty)$ representation of equation \eqref{eqn:wold} has
  $c(t) = 0$ and $A(0) = I$.
\end{definition}

@@

\begin{equation}
  \linEerr{x_i(t)}{\H_{t - 1}} < \linEerr{x_i(t)}{\H^{-j}_{t - 1}},
\end{equation}

@@

  \begin{enumerate}
    \item{$x_j \ngc x_i$}
    \item{$\forall \tau \in \N_+\ B_{ij}(\tau) = 0$ i.e. $\B_{ij}(z) = 0$}
    \item{$H_t^{i} \perp \H_{t - 1}^{j}\ |\ \H_{t - 1}^{-j}$}
    \item{$\linE{x_i(t)}{\H_{t - 1}^{-j}} = \linE{x_i(t)}{\H_{t - 1}}$}
  \end{enumerate}
\end{theorem}

@@

The edges of the Granger-causality graph $\gcg$ can be given a general
notion of ``weight'' by associating an edge $(j, i)$ with the
\textit{strictly causal} LTI filter $\B_{ij}(z)$ (see eqn
\eqref{eqn:filter_action}).  Thence, the matrix $\B(z)$ is analogous
to a \textit{weighted adjacency matrix}\footnote{\footnotesize We are using the
  convention that $\B_{ij}(z)$ is a filter with input $x_j$ and output
  $x_i$ so as to write the action of the system as $\B(z)x(t)$ with
  $x(t)$ as a column vector.  This competes with the usual convention
  for adjacency matrices where $A_{ij} = 1$ if there is an edge
  $(i, j)$.  In our case, the sparsity pattern of $\B_{ij}$ is the
  \textit{transposed} conventional adjacency matrix.} for the graph $\gcg$.  And,
in the same way that the $k^{\text{th}}$ power of an adjacency matrix
counts the number of paths of length $k$ between nodes,
$(\B(z)^k)_{ij}$ is a filter isolating the ``action'' of $j$ on $i$ at
a time lag of $k$ steps, this is exemplified in the inversion formula
\ref{eqn:lsi_inversion}.

@@

  where $\A(z) = \sum_{\tau = 0}^\infty A(\tau)z^{-\tau}$ is the filter from
  the Wold decomposition representation of $x(t)$, equation
  (\ref{eqn:wold}).
\end{proposition}

@@

  then $\H_t^{(i)} \perp \H_t^{(j)}$, that is,
  $\forall s, \tau \in \Z_+\ \E[x_i(t - s)x_j(t - \tau)] = 0$.  Moreover,
  this means that $j \npwgc i$ and $\linE{x_j(t)}{\H_t^i} = 0$.
\end{proposition}

\begin{remark}
  The possibility that there exist nodes sharing both $i$ and $j$ as
  ancestors is not excluded, the point being that the temporal nature
  of Granger-causality eliminates the problems caused by ``colliders''
  (in the language of Pearl's causal calculus
  \cite{pearl2009causality}) in static causal inference.
\end{remark}

\begin{remark}
  It is possible for components of $x(t)$ to be correlated at some
  time lags without resulting in pairwise causality.  For instance,
  the conclusion $j \npwgc i$ of Proposition
  \ref{prop:separated_ancestor_uncorrelated} will still hold even if
  $i \in \anc{j}$, since $j$ cannot provide any information about $i$
  that is not available from observing $i$ itself.
  % However, it is important to note that this is the case only if we
  % have direct access to $x(t)$.  That is, if we instead observed a
  % noisy version of $x$ (i.e. $\tilde{x}(t) = x(t) + n(t)$) the
  % observation of $\tilde{x}_j$ would enable conditionally improved
  % estimates of $\tilde{x}_i$, without there necessarily being any
  % causal flow in the underlying system $x(t)$.
\end{remark}

@@

  \begin{figure}[h]
    \centering
    \caption{Transcription Regulatory Networks}
    \label{fig:gene_networks}
    \begin{subfigure}[b]{0.45\textwidth}
      \caption{\textit{E.Coli} Network of
        \cite{discovering_graphical_Granger_causality_using_the_truncating_lasso_penalty}}
      \label{fig:gene_network1}
      \includegraphics[width=\linewidth, height=\linewidth]{ecoli_regulatory_network.png}
    \end{subfigure}
    \begin{subfigure}[b]{0.45\textwidth}
      \caption{\textit{Saccharomyces cerevisiae} Network of
        \cite{learning_genome_scale_regulatory_networks}}
      \label{fig:gene_network2}
      \includegraphics[width=\linewidth, height=\linewidth]{huge_gene_network.png}
    \end{subfigure}

@@

\begin{remark}
  As we have seen and as is true in much of statistics, confounding
  nodes pose challenges for Granger-causality.  However, as opposed to
  the causal calculus of \cite{pearl2009causality}, pairwise
  Granger-causality does not suffer any difficulty with so-called
  ``colliders'', that is, the topology $i \rightarrow k \leftarrow j$ will never result
  in $i \pwgc j$ or $j \pwgc i$.  This is evidently an advantage of
  the \textit{temporal} nature of Granger-causality -- there is no
  backwards causal flow along the edges of $\gcg$.
\end{remark}

@@

  \begin{align}
    \tau_0(\B) &= \text{inf }\{\tau \in \Z_+\ |\ b(\tau) \ne 0\},\\
    \tau_{\infty}(\B) &= \text{sup }\{\tau \in \Z_+\ |\ b(\tau) \ne 0\}.\\
  \end{align}

@@

In order to eliminate the possibility of a particular sort of
cancellation, an ad-hoc assumption is required.  Strictly speaking,
the persistence condition is not a necessary or sufficient condition
for the following, but cases where the following fails to hold, and
peristence \textit{does} hold, are unavoidable pathologies.

@@

  \begin{equation*}
    H_i(z)x_i(t) = \linE{x_i(t)}{\H_{t - 1}^i},
  \end{equation*}

@@

\begin{remark}
  Under the condition of persistence, the only way for Assumption
  \ref{ass:T_causality} to fail is through cancellation in the terms
  defining $T_{ij}(z)$.  For example, the condition is assured if
  $x(t)$ is persistent, and there is only a single confounder.
  Unfortunately, some pathological behaviour resulting from
  confounding nodes seems to be unavoidable without some assumptions
  about the parameters of the $MA(\infty)$ system defining $x(t)$.
\end{remark}

@@

\begin{remark}
  The importance of this result is that when $i \pwgc j$ is a result
  of a condounder $k$, then $i \pwgc j \iff j \pwgc i$.  This
  implies that in a strongly causal graph every bidirectional pairwise
  causality relation must be the result of a confounder.  Therefore,
  in a strongly causal graph, pairwise causality analysis is
  \textit{immune to confounding} (since we can safely remove all
  bidrectional edges).
\end{remark}

@@

Our simulation results are summarized in Table
\ref{tab:simulation_table}, with additional figures provided in the
supplementary material Section \ref{apx:simulation}.  It is clear that
the superior performance of PWGC in comparison to AdaLASSO is as a
result of limiting the false discovery rate.  It is unsurprising that
PWGC exhibits superior performance when the graph is an SCG, but even
in the case of more general DAGs, the PWGC heuristic is still able to
more reliably uncover the graph structure for small values of $q$.  We
would conjecture that for small $q$, random graphs are ``likely'' to
be ``close'' to SCGs in some appropriate sense.  As $q$ increases,
there are simply not enough edges allowed by the SGC topology for it
to be possible to accurately recover $\gcg$.

@@

We emphasize that the causality graph topology is one of the key
defining features of time series analysis in comparison to standard
multivariate regression and therefore advocate for further study of
how different topological assumptions may impact the recovery of
causality graphs.  For example, are there provable guarantees on the
error rate of PWGC when applied to non strongly-causal graphs?  Can
constraint systems or cunning adaptive weighting schemes impose useful
prior knowledge about graph topology for the LASSO algorithm?
Finally, the work of \cite{barnett2015granger} has established the
superiority of Granger-causality testing by state space models (as
opposed to pure autoregressions) in many cases.  Combining this work
with our PWGC algorithm (by modifying the approach described in
Section \ref{sec:pairwise_hypothesis_testing} to instead utilize
state-space Granger-causality testing) therefore is likely to enable
application to very large networks of time series data which are not
well approximated by finite $\VAR(p)$ models.

% \bibliography{\string~global_bib.bib}
\bibliography{\string~/Documents/academics/global_academics/global_bib}
\end{document}

>>>>

\documentclass{statsoc}
% \usepackage{mathtime}
\usepackage{ccfonts,eulervm}
\usepackage{tabularx}
\usepackage{xr}
\externaldocument{supplementary_material}
% ---------------------------------------------------------------------------------------------------------------------------------
% The statsoc style file is broken?
% I have copied this code straight from stack overflow
% https://tex.stackexchange.com/questions/351768/problem-with-statsoc-class-and-pdflatex
\usepackage{geometry}

@@

@@

\def\gc{\overset{\text{GC}}{\rightarrow}}  % Granger causality arrow
\def\ngc{\overset{\text{GC}}{\nrightarrow}}  % Negated Granger causality arrow
\def\pwgc{\overset{\text{PW}}{\rightarrow}}  % Pairwise Granger causality arrow
\def\npwgc{\overset{\text{PW}}{\nrightarrow}}  % Negated pairwise Granger causality arrow
\def\te{\overset{\mathcal{T}}{\rightarrow}}  % Transfer entropy arrow
\def\gcg{\mathcal{G}}  % Granger-causality graph
\def\gcge{\mathcal{E}}  % Graph edges
\def\VAR{\mathsf{VAR}}  % VAR(p) model
\def\MA{\mathsf{MA}}  % MA(p) model
\def\B{\mathsf{B}}  % Filter B
\def\wtB{\widetilde{\B}}  % General filter B
\def\A{\mathsf{A}}  % Filter A
\def\H{\mathcal{H}}  % Hilbert space

@@

\section{Introduction and Review}
\label{sec:introduction}
In this paper we study the notion of Granger-causality
\cite{granger1969investigating} \cite{Granger1980329} as a means of
uncovering an underlying causal structure in multivariate time series.
Though the underlying causality graph cannot be observed directly,
it's presence is inferred as a latent structure among observed
time series data.  This notion is leveraged in a variety of
applications e.g. in Neuroscience as a means of recovering
interactions amongst brain regions \cite{bressler2011wiener},
\cite{anna_paper2008}, \cite{david2008identifying}; in the study of
the dependence and connectedness of financial institutions
\cite{NBERw16223}; gene expression networks \cite{Fujita2007},
\cite{methods_for_inferring_gene_regulatory_networks_from_time_series_expression_data},
\cite{grouped_graphical_granger_modelling_for_gene_expression_regulatory_networks_discovery},
\cite{discovering_graphical_Granger_causality_using_the_truncating_lasso_penalty};
and power system design \cite{Misyrlis2016450}, \cite{yuan2014root}.

@@

The principle contributions of this paper are as follows: firstly, in
section \ref{sec:theory} we study \textit{pairwise} Granger-causality
relations, providing novel theorems connecting the structure of the
causality graph to the pairwise ``causality flow'' in the system, as
well as an interpretation in terms of the graph topology of the
sparsity pattern of matrices arising in the Wold decomposition,
generalizing in some sense the notion of ``feedback-free'' processes
studied by \cite{caines1975feedback} in close connection with
Granger-causality.  We establish sufficient conditions (sections
\ref{sec:strongly_causal_graphs}, \ref{sec:persistent_systems}) under
which a fully conditional Granger-causality graph can be recovered
from pairwise tests alone (sec \ref{sec:pairwise_algorithm}).  We
report a summary of simulation results in \ref{sec:simulation}, with
additional results reported in the supplementary material Section
\ref{apx:simulation}.  Our simulation results establish that there is
significant potential for improvement over existing methods, and that
the graph-topological aspects of time series analysis are relevant for
both theory and practice.  Concluding remarks on further open problems
and extensions are provided in Section \ref{sec:conclusion}.  The
proofs of each proposition and theorem are also relegated to the
supplementary material, simple corollaries have proofs included in the
main text.

@@

\begin{equation}
  \label{eq:hilbert_space_defn}
  \begin{aligned}
    \H_t^{(x)} &= \cl \{\sum_{\tau = 0}^p a_\tau^\T x(t - \tau)\ |\ a_\tau \in \R^n, p \in \N\} \subseteq L_2(\Omega)\\
    H_t^{(x)} &= \{a x(t)\ |\ a \in \R\} \subseteq L_2(\Omega),
  \end{aligned}
\end{equation}

where the closure is naturally in mean-square.  We will often omit the
superscript $x$ which should be clear from context.  Evidently these
spaces are separable, and as closed subspaces of a Hilbert space they
are themselves Hilbert.  We will denote the spaces generated in
analogous ways by particular components of $x$ as e.g.
$\H_t^{(i, j)}$, $\H_t^{i}$ or by all but a particular component as
$\H_t^{(-j)}$.

As a consequence of the Wold decomposition theorem (see
e.g. \cite{lindquist}), every WSS sequence has the moving average
$\MA(\infty)$ representation

@@

The Equations \eqref{eqn:wold}, \eqref{eqn:ar_representation} can be
represented as $x(t) = \A(z)v(t) = \B(z)x(t) + v(t)$ via the action
(convolution) of the operators (LTI filters)
$$\A(z) \defeq \sum_{\tau = 0}^\infty A(\tau)z^{-\tau}$$ and
$$\B(z) \defeq \sum_{\tau = 1}^\infty B(\tau)z^{-\tau},$$ where the
operator $z^{-1}$ is the back shift operator acting on
$\ell_2^n(\Omega, \mathcal{F}, \mathbb{P})$, that is:

@@

\begin{definition}[Basic Setup]
  \label{def:basic_setup}
  The process $x(t)$ is an $n$ dimensional wide sense stationary
  process having invertible $\VAR(\infty)$ representation
  \eqref{eqn:ar_representation} where $v(t)$ is sequentially
  uncorrelated and has a diagonal positive-definite covariance matrix.
  The $\MA(\infty)$ representation of Equation \eqref{eqn:wold} has
  $c(t) = 0$ and $A(0) = I$.
\end{definition}

@@

\begin{equation}
  \linEerr{x_i(t)}{\H_{t - 1}} < \linEerr{x_i(t)}{\H^{(-j)}_{t - 1}},
\end{equation}

@@

  \begin{enumerate}
    \item{$x_j \ngc x_i$}
    \item{$\forall \tau \in \N_+\ B_{ij}(\tau) = 0$ i.e. $\B_{ij}(z) = 0$}
    \item{$H_t^{i} \perp \H_{t - 1}^{(j)}\ |\ \H_{t - 1}^{(-j)}$}
    \item{$\linE{x_i(t)}{\H_{t - 1}^{(-j)}} = \linE{x_i(t)}{\H_{t - 1}}$}
  \end{enumerate}
\end{theorem}

@@

The edges of the Granger-causality graph $\gcg$ can be given a general
notion of ``weight'' by associating an edge $(j, i)$ with the
\textit{strictly causal} LTI filter $\B_{ij}(z)$ (see Equation
\eqref{eqn:filter_action}).  Thence, the matrix $\B(z)$ is analogous
to a \textit{weighted adjacency matrix}\footnote{\footnotesize We are using the
  convention that $\B_{ij}(z)$ is a filter with input $x_j$ and output
  $x_i$ so as to write the action of the system as $\B(z)x(t)$ with
  $x(t)$ as a column vector.  This competes with the usual convention
  for adjacency matrices where $A_{ij} = 1$ if there is an edge
  $(i, j)$.  In our case, the sparsity pattern of $\B_{ij}$ is the
  \textit{transposed} conventional adjacency matrix.} for the graph $\gcg$.  And,
in the same way that the $k^{\text{th}}$ power of an adjacency matrix
counts the number of paths of length $k$ between nodes,
$(\B(z)^k)_{ij}$ is a filter isolating the ``action'' of $j$ on $i$ at
a time lag of $k$ steps, this is exemplified in the inversion formula
\eqref{eqn:lsi_inversion}.

@@

  where $\A(z) = \sum_{\tau = 0}^\infty A(\tau)z^{-\tau}$ is the filter from
  the Wold decomposition representation of $x(t)$, Equation
  \eqref{eqn:wold}.
\end{proposition}

@@

  then $\H_t^{(i)} \perp \H_t^{(j)}$, that is,
  $\forall s, \tau \in \Z_+\ \E[x_i(t - s)x_j(t - \tau)] = 0$.  Moreover,
  this means that $j \npwgc i$ and $\linE{x_j(t)}{\H_t^{(i)}} = 0$.
\end{proposition}

\begin{remark}
  It is possible for components of $x(t)$ to be correlated at some
  time lags without resulting in pairwise causality.  For instance,
  the conclusion $j \npwgc i$ of Proposition
  \ref{prop:separated_ancestor_uncorrelated} will still hold even if
  $i \in \anc{j}$, since $j$ cannot provide any information about $i$
  that is not available from observing $i$ itself.
\end{remark}

@@

  \begin{figure}[h]
    \centering
    \caption{Transcription Regulatory Networks}
    \label{fig:gene_networks}
    \begin{subfigure}[b]{0.45\textwidth}
      \caption{\textit{E.Coli} Network of
        \cite{discovering_graphical_Granger_causality_using_the_truncating_lasso_penalty}}
      \label{fig:gene_network1}
      \includegraphics[width=\linewidth, height=\linewidth]{ecoli_regulatory_network.pdf}
    \end{subfigure}
    \begin{subfigure}[b]{0.45\textwidth}
      \caption{\textit{Saccharomyces cerevisiae} Network of
        \cite{learning_genome_scale_regulatory_networks}}
      \label{fig:gene_network2}
      \includegraphics[width=\linewidth, height=\linewidth]{huge_gene_network.pdf}
    \end{subfigure}

@@

@@

  \begin{align}
    \tau_0(\B) &= \text{inf }\{\tau \in \Z_+\ |\ b(\tau) \ne 0\},\\
    \tau_{\infty}(\B) &= \text{sup }\{\tau \in \Z_+\ |\ b(\tau) \ne 0\}.
  \end{align}

@@

In order to eliminate the possibility of a particular sort of
cancellation, an ad-hoc assumption is required.  Strictly speaking,
the persistence condition is not a necessary or sufficient condition
for the following, but cases where the following fails to hold, and
persistence \textit{does} hold, are unavoidable pathologies.

@@

  \begin{equation*}
    H_i(z)x_i(t) = \linE{x_i(t)}{\H_{t - 1}^{(i)}},
  \end{equation*}

@@

\begin{remark}
  Under the condition of persistence, the only way for Assumption
  \ref{ass:T_causality} to fail is through cancellation in the terms
  defining $T_{ij}(z)$.  For example, the condition is assured if
  $x(t)$ is persistent, and there is only a single confounder.
  Unfortunately, some pathological behaviour resulting from
  confounding nodes seems to be unavoidable without some assumptions
  about the parameters of the $\MA(\infty)$ system defining $x(t)$.
\end{remark}

@@

\begin{remark}
  The importance of this result is that when $i \pwgc j$ is a result
  of a confounder $k$, then $i \pwgc j \iff j \pwgc i$.  This
  implies that in a strongly causal graph every bidirectional pairwise
  causality relation must be the result of a confounder.  Therefore,
  in a strongly causal graph, pairwise causality analysis is
  \textit{immune to confounding} (since we can safely remove all
  bidirectional edges).
\end{remark}

@@

Our simulation results are summarized in Table
\ref{tab:simulation_table}, with additional figures provided in the
supplementary material Section \ref{apx:simulation}.  It is clear that
the superior performance of PWGC in comparison to AdaLASSO is as a
result of limiting the false discovery rate.  It is unsurprising that
PWGC exhibits superior performance when the graph is an SCG, but even
in the case of more general DAGs, the PWGC heuristic is still able to
more reliably uncover the graph structure for small values of $q$.  We
would conjecture that for small $q$, random graphs are ``likely'' to
be ``close'' to SCGs in some appropriate sense.  As $q$ increases,
there are simply not enough edges allowed by the SCG topology for it
to be possible to accurately recover $\gcg$.

@@

We emphasize that the causality graph topology is one of the key
defining features of time series analysis in comparison to standard
multivariate regression and therefore advocate for further study of
how different topological assumptions may impact the recovery of
causality graphs.  For example, are there provable guarantees on the
error rate of PWGC when applied to non strongly-causal graphs?  Can
constraint systems or cunning adaptive weighting schemes impose useful
prior knowledge about graph topology for the LASSO algorithm?
Finally, the work of \cite{barnett2015granger} has established the
superiority of Granger-causality testing by state space models (as
opposed to pure autoregressions) in many cases.  Combining this work
with our PWGC algorithm (by modifying the approach described in
Section \ref{sec:pairwise_hypothesis_testing} to instead utilize
state-space Granger-causality testing) therefore is likely to enable
application to very large networks of time series data which are not
well approximated by finite $\VAR(p)$ models.  Moreover, our
heuristics are in principle applicable in a model-free context.  As
long as a primitive for testing the pairwise causation between two
components of a multivariate time series is available, our methods may
be useful.

\bibliography{paper_bib}
\end{document}
